---
title: Monte Carlo Simulation (*F* Distribution)
author: Michael A. Seaman, University of South Carolina
---

This is a Monte Carlo simulation of the t test coverage
of the mean when samples are from the F distribution.

I'm setting up some parameters that I can easily change,
so I'm putting those right at the top. I'm starting with
some initial values to demonstrate.

```{r}
sample.size <- 20
degrees.1 <- 2
degrees.2 <- 10
conf.level <- .95
num.rep <- 100
```

This is a function for a single replication. You must
supply the sample size, degrees of freedom (1 and 2)
and the confidence level.

```{r}
MonteF <- function(n, df1, df2, ci.level){

  mean.f = df2/(df2-2)
  f.sample <- rf(n, df1, df2)
  t.result <- t.test(f.sample, conf.level = ci.level)
  ci.lb <- t.result$conf.int[1]
  ci.ub <- t.result$conf.int[2]
  
  if ((mean.f > ci.lb) & (mean.f < ci.ub)) result <- 1 else result <- 0
  
  MonteF.out <- vector()
  
  MonteF.out[1] <- ci.lb
  MonteF.out[2] <- ci.ub
  MonteF.out[3] <- result
  
  return(MonteF.out)
  
}
```

Next I'm going to call the function with the demonstration
parameters set above.

```{r}
F.results <- replicate(num.rep,
                       MonteF(sample.size,
                              degrees.1,
                              degrees.2,
                              conf.level))
```

I'm going to show these results, but you probably wouldn't want
to do this if you use a large number of replications. I'm just
demonstrating how they could look.

```{r}
F.results
```


I'm going to tabulate the results.

```{r}
prop.coverage <- sum(F.results[3,])/num.rep
```

Finally, I'm going to show this coverage rate.

```{r}
prop.coverage
```

